### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
Minor fixes. Version sent to Phys. Coord. and LF.
Added affiliation to CERN
Fixed missing bar in the D0*-bar D0 for the X(3872)

F. Bellini and A. Kalweit

16th of May 2018
\end{center}

@@

\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
,    
\label{eq:BA}
\end{equation}
anielski-HQ14
\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872). In fact, if the X(3872) corresponds to a loosely bound $D^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton. Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton. Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.

>>>>

F. Bellini$^{1}$ and A. Kalweit$^{1}$
\\$^{1}$CERN, Switzerland
\medskip

12th July 2018
\end{center}

@@

\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{Z}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.\;
   \left(E_{\mathrm{n}}\frac{\mathrm{d}^{3}N_{\mathrm{n}}}{\mathrm{d}p_{\mathrm{n}}^{3}}\right)^{N}}\left\vert_{\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.\;
,    
\label{eq:BA}
\end{equation}

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since in the LHC collision energy regime the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}. As a consequence, also the anti-particle to particle ratio for the light (hyper-)nuclei considered in this work is measured to be consistent with unity in pp, p--Pb and Pb--Pb collisions \cite{ALICE:nucleipp2017, anielski-HQ14, Acharya:2017dmc, Adam:2015yta}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, anielski-HQ14}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{Acharya:2017dmc}.

@@

In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872). In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton. Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton. Additional theoretical studies and numerical predictions are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects might become experimentally accessible.
